\huge Tor's Usability for Censorship Circumvention

### 2016-04-23 pets2017-paper/pets2017-paper.tex
Manually hack in better scales for the all-participant-edges graphic.
I did this just by editing the original graphic in Inkscape. This
version isn't automatically regenerated, so we have to remember to
re-edit the graphic if the underlying data change.
Spell check.

In addition to tor-specific components, a proxy may be necessary to connect 
outside the local network in certain managed networks, such as corporate or university networks.
Configuring a proxy requires providing the proxy protocol, ip address, port and additional optional
fields. There is no assistance or automation with this process. The user must locate the 
proxy information and correctly format this information into the configuration interface.

@@

\begin{figure*}
\centering
\includegraphics{all-participant-edges}
\caption{
Summary of participants' actions throughout the entire experiment.
Different colors indicate which screen was shown at each moment.
The narrow black lines show the times when the configuration interface
was not running; i.e., a participant was doing something else
such as searching the web in another browser.
The overall length of the lines show the total time to completion,
except for those we cut off after approximately 40 minutes.
}
\label{fig:all-participant-edges}
\end{figure*}

@@

We discarded data on participants who chose to download their own version of Tor Browser online. Some downloaded their own version without trying the provided one on their desktop, while others did so after feeling frustrated with the provided version. Appendix~\ref{tor-downloads} gives the unfortunate details the of where Tor was downlaoded when torproject.org was blocked.

>>>>

In addition to Tor-specific components, a proxy may be necessary to connect 
outside the local network in certain managed networks, such as corporate or university networks.
Configuring a proxy requires providing the proxy protocol, IP address, port and additional optional
fields. There is no assistance or automation with this process. The user must locate the 
proxy information and correctly format this information into the configuration interface.

@@

\begin{figure*}
\centering
% This is a manually edited version of the automatically generated
% all-participant-edges graphic. It is edited to have better scale labels for
% the treatments.
\includegraphics{all-participant-edges-scales}
\caption{
Summary of participants' actions throughout the entire experiment.
Different colors indicate which screen was shown at each moment.
The narrow black lines show the times when the configuration interface
was not running; i.e., a participant was doing something else
such as searching the web in another browser.
The overall length of the lines show the total time to completion,
except for those we cut off after approximately 40 minutes.
}
\label{fig:all-participant-edges}
\end{figure*}

@@

We discarded data on participants who chose to download their own version of Tor Browser online. Some downloaded their own version without trying the provided one on their desktop, while others did so after feeling frustrated with the provided version. Appendix~\ref{tor-downloads} gives the unfortunate details of where Tor was downloaded when torproject.org was blocked.
